% LaTeX resume using res.cls
\documentclass[line,letterpaper]{resume}
\usepackage{scalefnt}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
%Default
%\usepackage[scale=1]{tgschola}
%Kurier
%\usepackage[math]{kurier}
%\usepackage[T1]{fontenc}
%\usepackage{ascii}
%\usepackage[T1]{fontenc}

\usepackage{multirow}
\hypersetup{colorlinks=false, pdfborder={0 0 0}}
\begin{document}

\name{\textbf{Nathan Aclander} \ \ \ \ \ \ \
      \textit{\href{www.aclander.com}{www.aclander.com}} \ \ \ \ \ \ \
      \textit{\href{mailto:nathan.aclander@gmail.com}{nathan.aclander@gmail.com}} \ \ \ \ \ \ \
      \textit{(949)-436-8945}}
\address{\ }
\address{\ }


\begin{resume}
    \vspace{-24pt}
    \section{\uppercase{Education}} {\sl Bachelor of Science,} \/
    Computer Science \& Engineering \\
    \underline{\href{http://cs.ucla.edu}{University of California, Los Angeles}}\\
    \vspace{-16pt}

 \section{\uppercase{Skills}}
    {\sl\textbf{Overview:}}\/
	\begin{itemize}
		\item Experience in writing clean reliable software, at scale
		\item Experience in administration and operation of multi-region distributed systems
	\end{itemize}
    {\sl\textbf{Languages:}}\/
    Python, Ruby, Java, Bash, C, Emacs Lisp, C++, GO \\
    {\sl\textbf{Frameworks:}}\/
	Ruby on Rails, Flask, Spring, various AWS services\\
    {\sl\textbf{Operating Systems:}}\/
	Administrating and developing on Linux (RHEL/Debian/Arch) and Unix environments at scale\\
    {\sl\textbf{Software:}}\/
	\sout{Vim} Emacs, Git, Mercurial, SVN, Redmine
    \vspace{-6pt}

	\section{\uppercase{Work Experience}}

	{\sl\textbf{\href{https://cloud.oracle.com/}{Oracle Cloud Infrastructure}}} \hfill Winter 2018--Present\\
    \emph{Senior member of Technical Staff } --- Part of the Data Center Automation team.
    Developed a workflow as a service solution to automate hardware ingestion into OCI
    datacenters. Currently expanding service to other internal customers.

	{\sl\textbf{\href{https://aws.amazon.com/}{Amazon - AWS}}} \hfill Winter 2015--Winter 2018\\
    \emph{SDE I / II } --- At \underline{\href{http://aws.amazon.com/ec2}
	{Amazon EC2}} where I was part of the Kernel and Operating System team. I helped
	develop next generation EC2 instances. I then worked on the EC2 Tools team,
        developing provisioning and configuration systems.

	{\sl\textbf{\href{www.amazon.com}{Amazon}}} \hfill Summer 2014--Fall 2014\\
    \emph{SDE Intern} --- At \underline{\href{https://www.amazon.jobs/en/teams/infosec}
    {Amazon Information Security}} where I developed an internal tool designed to
	enable employees throughout the company to manage preferences regarding the
	security state of their code.

    {\sl\textbf{\href{www.directv.com}{DIRECTV}}} \hfill Summer 2013-- Fall 2013\\
    \emph{Software Engineering Intern}
    ---  Developed memory leak detection tool for custom linux userland tools,
	with cross architecture compatability(ARM, MIPS, X86)

    {\sl\textbf{\href{https://uclaradio.com}{UCLA Radio}}} \hfill Fall 2011-- Fall 2014\\
    \emph{Web Director} --- UCLA Radio website group leader, website administrator

    {\sl\textbf{\href{https://housing.ucla.edu/residence-hall-computing}
	{Student Technology Center}}} \hfill Summer 2011-- winter 2014\\
    \emph{Computer Technician} --- Customer Support Representative,
IT support (software and hardware), network infrastructure support
    \vspace{-6pt}


    \section{\uppercase{Independent Projects}}
	\begin{itemize}
        \item \underline{\href{https://aclander.com/home_lab.svg}
            {Multi-vlan home network}} configuration using shorewall for zone management
          and elasticsearch for network telemetry
        \item
        \underline{\href{https://tinyurl.com/la495b3}{Various contributions}}
        to emacs packages and ecosystem.
	\item \underline{\href{https://github.com/naclander/uploader}{Uploader}} -
	A tool to help people share files and links.
	\item Front/Back end development for uclaradio.com, including layout design
	      and feature implementation.
	\item Experience Building single threaded and multithreaded server software
	      in C, Twisted, and Node.js.
	\item Large scale software development; multithreaded implementation of GZIP
	      in Java. Reimplementation of the Pacman video game.
	\item Anti-theft Android App development using Google App Engine.
	\end{itemize}
    \vspace{-6pt}

    \hfill \emph{For more projects and contributions see
    \underline{\href{https://github.com/naclander}{naclander on github}}}.

    \vspace{-15pt}

\section{\uppercase{Extra-Curricular}}
    {\sl\textbf{\href{https://www.uwhuskytech.com/}{Husky Tech}}} \hfill Winter 2019 \\
      \emph{Industry Mentor} --- Volunteered to mentor University of Washington Students
      using my personal experience in industry. Was able to provide advice and guidance to
      navigating a University CS programs, internships, and industry jobs.

    {\sl\textbf{\href{http://linux.ucla.edu}{Linux Users Group}}} \hfill Fall 2013 -- Spring 2014\\
    \emph{Vice President} --- A student organization at UCLA to help promote
	and familiarize other students with the installation and usage of Linux
	operating systems and other open source projects, both for school and for personal use.


   \end{resume}
\end{document}


